\pkg{cubble}: An R Package for Structuring Spatio-temporal Data

### 2022-01-17 3-advanced.Rmd
section on glyph map

>>>>

## Glyph map

Glyph map [@Wickham2012-yr] plots the time series as single glyph on the map. 
<!-- Variation of glyph maps has been developed to visualise uncertainty in **Visumap** [@Lucchesi2021] and deal with irregular local grid [@Beecham2021-vk].  -->
In \proglang{R}, `GGally` implements the glyph map through the `glyphs()` function, which outputs a data frame with calculated position (`gx`, `gy`, `gid`) of each point on the time series given the major and minor xy variable using linear algebra (Equation 1 and 2 in @Wickham2012-yr). The data can then be piped into `ggplot` to create the glyph map:

```{r eval = FALSE, echo = TRUE}
library(ggplot2)
gly <- glyphs(data, 
              x_major = ..., x_minor = ..., 
              y_major = ..., y_minor = ..., ...)

ggplot(gly, aes(gx, gy, group = gid)) + 
  geom_path() 
```

While this calculation can be seen as part of the `setup_data()` in a `ggproto`. A re-implementation of the glyph map as `GeomGlyph` has been made in `cubble` to create the glyph map with `geom_glyph`:

```{r eval = FALSE, echo = TRUE}
ggplot(data = data) +
  geom_glyph(aes(x_major = ..., x_minor = ..., 
                 y_major = ..., y_minor = ...))
```

Polar glyph map can be specify as a parameter, `polar = TRUE`, in the `geom_glyph()`, along with `width` and `height` in either absolute or relative value. Global and local scale can also be controlled by the parameter `global_rescale`, which default to `TRUE`. Reference box and line can be added with separate `geom_glyph_box()` and `geom_glyph_line()`.

### 2022-01-17 main.tex
section on glyph map

>>>>

\hypertarget{glyph-map}{%
\subsection{Glyph map}\label{glyph-map}}

Glyph map \citep{Wickham2012-yr} plots the time series as single glyph
on the map. In \proglang{R}, \texttt{GGally} implements the glyph map
through the \texttt{glyphs()} function, which outputs a data frame with
calculated position (\texttt{gx}, \texttt{gy}, \texttt{gid}) of each
point on the time series given the major and minor xy variable using
linear algebra (Equation 1 and 2 in \citet{Wickham2012-yr}). The data
can then be piped into \texttt{ggplot} to create the glyph map:

\begin{CodeChunk}
\begin{CodeInput}
R> library(ggplot2)
R> gly <- glyphs(data, 
+               x_major = ..., x_minor = ..., 
+               y_major = ..., y_minor = ..., ...)
R> 
R> ggplot(gly, aes(gx, gy, group = gid)) + 
+   geom_path() 
\end{CodeInput}
\end{CodeChunk}

While this calculation can be seen as part of the \texttt{setup\_data()}
in a \texttt{ggproto}. A re-implementation of the glyph map as
\texttt{GeomGlyph} has been made in \texttt{cubble} to create the glyph
map with \texttt{geom\_glyph}:

\begin{CodeChunk}
\begin{CodeInput}
R> ggplot(data = data) +
+   geom_glyph(aes(x_major = ..., x_minor = ..., 
+                  y_major = ..., y_minor = ...))
\end{CodeInput}
\end{CodeChunk}

Polar glyph map can be specify as a parameter, \texttt{polar\ =\ TRUE},
in the \texttt{geom\_glyph()}, along with \texttt{width} and
\texttt{height} in either absolute or relative value. Global and local
scale can also be controlled by the parameter \texttt{global\_rescale},
which default to \texttt{TRUE}. Reference box and line can be added with
separate \texttt{geom\_glyph\_box()} and \texttt{geom\_glyph\_line()}.
